Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-01-13 main.tex
Some more thoughts

\bcp{
  \begin{itemize}
  \item A {\em property} is a function that takes a contour to a
  prefix-closed set of (finite and/or infinite) sequences of machine states.
  That is, it takes a starting contour and produces a checker that tells
  whether a given trace is OK to observe.
  \item A policy $p$ {\em guarantees} a property $P$ if, for each contour
  $\contour$, the sequence of machine states obtained by projecting the
  sequence of ..... ARGH WHAT ABOUT VARIANTS!?!
  \item Proposal: Forget about full-blown NI and make the whole paper be
  about ``lockstep NI'' where the PC is the same in every pair of
  related runs
  \begin{itemize}
  \item One issue that I am not sure about: Could there be a sneaky way of
  ``putting secret information into the control state'' where the PCs of
  related runs are always in lockstep but, because the instruction memory is
  writeable, different instructions can get dispatched.  E.g., XXXX
  \item So maybe we should be asking that the instruction stream be
  identical, not (just?) the PCs
  \item One nice observation is that, if we are only interested in pairs of
  runs with identical PCs, there are two different ways to proceed: (1) say
  that we {\em ignore} runs where the PCs (or instruction streams) diverge
  (e.g., taint tracking), or (2) {\em disallow} runs where the PCs (or
  instruction streams) diverge, i.e., demand that this never happens (e.g.,
  stack and heap policies).
  \end{itemize}
  \item A remaining question is what to do about the possibility that the
  contour changes differently on two related runs.  We could disallow this,
  but not certain it's necessary---maybe everything works out OK.
  \end{itemize}
}

>>>>

\bcp{Sketchy / out of date from here on...}

  \begin{itemize}
  \item A {\em property} is a function that takes a contour to a
  prefix-closed set of (finite and/or infinite) sequences of machine states.
  That is, it takes a starting contour and produces a checker that tells
  whether a given trace is OK to observe.
  \begin{itemize}
  \item I am not sure whether we want to be talking in terms of {\em
    properties} or {\em hyperproperties} here (and all the way through).
  \end{itemize}
  \item Proposal: Forget about full-blown NI and focus the whole paper on
  variants of ``lockstep NI'' where the PC is the same in every pair of
  related runs.
  \begin{itemize}
  \item One issue that I am not sure about: Could there be a sneaky way of
  ``putting secret information into the control state'' where the PCs of
  related runs are always in lockstep but, because the instruction memory is
  writeable, different instructions can get dispatched.

  E.g., suppose the program looks like
\begin{verbatim}
0:   load from address 1000
     write to address 100
     jump to address 100
100: <initial contents don't matter>
     write R3 into address 1004
     jump to address 100
1000: <marked HIGH so that initial
       contents vary on different runs>
1004: <marked OBSERVABLE>
\end{verbatim}
  If the initial contents of address 1000 in one run is the encoding of the
  instruction ``load immediate 0 into R3'' and the initial contents in the
  other run is the encoding of the instruction ``load immediate 1 into R3,''
  then the two programs execute different instructions (leading them to
  write different things to an observable location) even though their PCs
  are always in lock step.

  \item So maybe we should be asking that the instruction stream be
  identical, not (just?) the PCs
  \end{itemize}
  \item One nice observation is that, if we are only interested in pairs of
  runs with identical PCs, there are two different ways to proceed: (1) say
  that we {\em ignore} runs where the PCs (or instruction streams) diverge
  (e.g., taint tracking), or (2) {\em disallow} runs where the PCs (or
  instruction streams) diverge, i.e., demand that this never happens (e.g.,
  stack and heap policies).
  \item A remaining question is what to do about the possibility that the
  contour changes differently on two related runs.  We could disallow this,
  but not certain it's necessary---maybe everything works out OK.
  \end{itemize}
